Page not found

### 2023-06-21 manuscript/chapters/1_intro.qmd
guess who just did rm ../docs -r but accidentally had their inkscape svg figures saved in docs instead of manuscript ???? IT MEEEE AM SO SILLYYYYYYYYYY

![(TODO add phi, add z instead of xi, arrow only in one direction) Every neuron in a rate neural network has a position in the $p$-dimensional embedding space](figures/neural_field_discrete.png)

@@

$$
\partial_t h(\vec z, t) = -h(\vec z, t) + \int_{\mathbb{R}^p} w(\vec z, \vec y) \phi(h(\vec y, t)) \rho(\mathrm d \vec y).
$$ {#eq-nf}

![(TODO add phi, add z instead of xi) The connectivity kernel defines the influence between localized neural populations in the embedding space](figures/connectivity_kernel.png)

>>>>

![Every neuron in a rate neural network has a position in the $p$-dimensional embedding space](figures/fig-rnn.svg){width=500px}

@@

$$
\partial_t h(\vec z, t) = -h(\vec z, t) + \int_{\mathbb{R}^p} w(\vec z, \vec y) \phi(h(\vec y, t)) \rho(\mathrm d \vec y).
$$ {#eq-nf}
<!-- 
![(TODO add phi, add z instead of xi) The connectivity kernel defines the influence between localized neural populations in the embedding space](figures/connectivity_kernel.png) -->

### 2023-06-21 manuscript/chapters/3_mappings.qmd
guess who just did rm ../docs -r but accidentally had their inkscape svg figures saved in docs instead of manuscript ???? IT MEEEE AM SO SILLYYYYYYYYYY

![(TODO) Embedding of the population dynamics in $[0,1]$](figures/photo_2023-06-10_19-26-49.jpg){#fig-popdynamics-01}

@@

![(TODO, reorder args of $w_U$) Every point of the grid effectively performs coarse-graining, and defines a point where we sample the connectivity kernel $w_U$ and the 2D neural field $h_U$](figures/photo_2023-06-10_21-13-23.jpg){#fig-grid-sampling}

@@

![(TODO) Venn diagram reprensenting the properties of functions $[0,1] \mapsto [0,1]^2$ which are allowed by Netto's theorem.](figures/photo_2023-06-18_21-32-45.jpg){width=400px #fig-venn}

@@

![(TODO rename bins to segments) Splitting $[0,1]$ recursively gives the binary bit expansion of $v_1$](figures/photo_2023-06-10_17-21-28.jpg){#fig-recurse-binary}

@@

![(TODO) Averaging $2^n$ of the $4^n$ segments populations of $S^n$ results in the $2^n$ segments populations](figures/photo_2023-06-13_12-15-32.jpg){width=400px #fig-averaging}

>>>>

![Embedding of the population dynamics in $[0,1]$](figures/fig-multipop.svg){width=500px #fig-popdynamics-01}

@@

![Every point of the grid effectively performs coarse-graining, and defines a point where we sample the connectivity kernel $w_U$ and the 2D neural field $h_U$](figures/fig-smallsquare.svg){width=500px #fig-grid-sampling}

@@

![Venn diagram reprensenting the properties of functions $[0,1] \mapsto [0,1]^2$ which are allowed by Netto's theorem.](figures/fig-venn.svg){width=400px #fig-venn}

@@

![Splitting $[0,1]$ recursively with the indicator function gives the binary bit expansion of $v_1$](figures/fig-binary.svg){width=400px #fig-recurse-binary}

@@

![Averaging $2^n$ of the $4^n$ segments populations of $S^n$ results in the $2^n$ segments populations](figures/fig-cg.svg){width=400px #fig-averaging}
